---
title: "Pushups"
author: "Emporer of all that is seen"
date: "October 24, 2016"
output: html_document
---

```{r include=FALSE}
require(knitr)
require(mosaic)
require(tigerstats)
```

# Introduction

Several years ago some MAT 111 students who were on the footbal team conducted a study of their team-mates.  The results are contained in the data frame `pushups` in the `tigerstats` package.

Two football players at GC asked their team-mates to do as many pushups as they could in two minutes.

Format

A data frame with 30 observations on the following 3 variables.

weight
weight of subject in pounds.

pushups
number of pushups completed.

position
a factor with levels LINE SKILL: type of position played by the subject. Line positions require high body mass, skill positions require a lot of running around.


$H_0$: null hypothis is ....   
$H_A$: alternative hypotheses...   

```{r include=FALSE}
data(pushups)
View(pushups)
help(pushups)
```

Among other things, the students recorded the type of position a player had on the team (either line or skill), and also the number of push-ups each player could perform in a two-minute period.

Line players are on the offensive or defensive line.  They need to be a certain kind of speed, but they must also be quite big and strong.  Skill players do a lot of runninga and catching:  they are the quarterback, running backs, receivers, etc.

Our Research Question is:

  >Who does more pushups, on average: a line player or a skill player?


# Methods

<Perform a variable analysis, and based on that nalysis choose at least one apprpriate graphical method and one appropriate numerical method to address the research question.>

You fill in the methods stuff here

# Results

<You have both graphical and numerical methods, so you will have both graphical and numerical results to consider.>

## Graphical Results

<Your graph should have a good title, and axes should be labled as needed.  Discuss your graphical results, showing how they answer the research question.  Use specific features of the graph in your discussion.>


pushups

## Numerical Results

<Discuss only the features of your numericla output that are relvant to answerting the Research Question.  Mention these features explicitly in your discussion.>

do a t-test here...

```{r}

```





# Discussion and Conclusion

<State your overall conclusion.  This is also a good place to mention other Research Questions that came to mind as you were carrying out this study.>